---
title: "Usage Examples"
author: "Nick R. Bachelder"
date: "2023-01-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(tidycensus)
library(acs)
library(dplyr)
library(leaflet)
library(rgdal)
library(sp)
library(sf)
library(dplyr)
library(ggplot2)
library(shiny)
library(DT)
library(ggrepel)
library(tidyr)
library(shinycssloaders)
library(shinythemes)
library(SwimmeR)
library(lubridate)
library(maptools)
library(readr)
library(rgeos)
library(readxl)
library(here)
library(viridis)
library(reshape2)
setwd(here::here())

source(paste0(here::here(), '/functions/ses_pull_functions.R'))
source(paste0(here::here(), '/functions/ses_plot_functions.R'))
```

# Run census api key to pull (NOTE: only need to do this once).

In order to obtain a tidycensus key, visit http://api.census.gov/data/key_signup.html
```{r}
# census_api_key("INSERT CODE HERE",
#                overwrite=T, install=T)
```

# Specify Needed Years and Codes

Possible values for geo: county ("county"), zip code ("zcta"), many more found at https://walker-data.com/tidycensus/articles/basic-usage.html

```{r}
needed_years <- seq(2011, 2013, by = 1)
geo <- "zcta"
```


# Pull SES data

Possible years are dependent on geographical input: For zcta (2011 - 2021), for county (2009 - 2021).

After running this line, variables removed due to incompleteness for any of the years (ie. variables not taken during year x) are listed.

This code chunk may take a few minutes, dependent on how many years of data are being pulled.
```{r}
# get codes from excel file found in codes_data folder
my_codes <- get_existing_codes(years = needed_years, file_path = paste0(here::here(), '/codes_data/acs_2014_codes_updated.csv')) 

# pull data
dat_all <- get_multiple_ACS(years = needed_years, codes = my_codes, geo = geo)
dat_all
```


## MAPPING

Note plotting can only be done with geographies "zcta", or "county".

Below pulls in appropriate shape plot

```{r}
if (geo == "zcta"){
  shape <- readOGR(here::here('codes_data/shape_save_zcta'), layer = 'zcta_shape_save')
  shape@data <- shape@data %>% dplyr::rename('zcta' = 'ZCTA5CE10')
}
if (geo == "county"){
  shape <- readOGR(here::here('codes_data/shape_save_county'), layer = 'county_shape')
}
```

# leaflet state plot example
```{r}
# Also Try: States = "All'
# You can drag below
get_leaflet(dat_all = dat_all, states = 'NC', years ="2011", attribute = 'age_over_65_prop', geo = geo)
```


# state ggplot example
```{r}
get_geom_poly(dat_all = dat_all, states = 'PA', years = '2013', attribute = 'age_over_65_prop', geo = geo)
```

# state ggplot progression example
```{r}
see_year_progression(dat_all = dat_all, states = 'PA', attribute = 'age_over_65_prop', geo = geo, years = needed_years)
```



# Run below line if you want to see all possible census variables (1045 topics, some seperated by age, etc). Previously used variables are found and used in the data_codes folder, but more can be added (Note: if you would like to do this, more cleaning may be neccecary in the pull function)

```{r}
# load_variables(2015, "acs5", cache = TRUE)$concept %>% unique()
```











